Is high social class always beneficial for survival? A study of northern Sweden 1801--2013 \footnote{Short; "Is high social class beneficial for survival?"} \footnote{Funding:}

### 2018-09-26 popstud_open.Rmd
fix Appendix and Figure 3

```{r plottaalla,fig.height = 8, out.height = "18cm", fig.cap="Exposure by social class (from the top: elite, middle, workers, farmers, none), time period, and sex.", fig.scap="Exposure by social class, time period, and sex"}
cls <- rainbow(5, s = 1.0)
cls <- cls[c(2, 3, 1, 5, 4)]
cls[1] <- "black"

oldpar <- par(mfrow = c(2, 1))
barplot(t(yy)[5:1, ], col = cls, las = 2, ylab = "Per cent", main = "Men")
barplot(t(yy2)[5:1, ], col = cls, las = 2, ylab = "Per cent", main = "Women")
par(oldpar)
```

@@

>>>>

```{r plottaalla,fig.height = 8, out.height = "18cm", fig.cap="Relative exposure by social class (from the top: elite, middle, workers, farmers, none), time period, and sex.", fig.scap="Exposure by social class, time period, and sex"}
cls <- rainbow(5, s = 1.0)
cls <- cls[c(2, 3, 1, 5, 4)]
cls[1] <- "black"

oldpar <- par(mfrow = c(2, 1))
barplot(t(yy2)[5:1, ], col = cls, las = 2, ylab = "Per cent", main = "Women")
barplot(t(yy)[5:1, ], col = cls, las = 2, ylab = "Per cent", main = "Men")
par(oldpar)
```

@@

# Appendix {-}

Figure 3 is shown as absolute numbers, exposures for women in Table \@ref(tab:womenexp), and exposures for men in Table \@ref(tab:menexp).

```{r exposuretab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
ex <- with(vb, tapply(exposure, list(period, hisclass, sex), sum))
print(xtable(ex[,,2], label = "tab:womenexp", caption = "Exposure in years by hisclass and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r exposuretab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(ex[,,1], label = "tab:menexp", caption = "Exposure in years by hisclass and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```

Then number of deaths for women are shown in Table \@ref(tab:womendeaths), and for men in Table \@ref(tab:mendeaths).

```{r deathtab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
deaths <- with(vb, tapply(event, list(period, hisclass, sex), sum))
print(xtable(deaths[,,2], label = "tab:womendeaths", caption = "Number of deaths by hisclass and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r deathtab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(deaths[,,1], label = "tab:mendeaths", caption = "Number of deaths by hisclass and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```
